---
title: "remove-false-positives"
author: "Andrew Edwards"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{remove-false-positives}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Simple example

The object `small_example` has one mock sample and three non-mock samples, with four
mock species in the mock sample and three non-mock species. *Update if change
terminology*. The first column identifies the sample, and remaining columns are
m1, m2, m3 and m4 for the four mock species, and 1, 2 and 3 for the non-mock species.
Corresponding entries are the number of reads of each species in each sample.

```{r, echo=TRUE, results='asis'}
knitr::kable(small_example)      # kable() is just to display the result for this vignette
```

To remove the false positives use the function `remove_false_pos()`:

```{r, echo=TRUE, results='asis'}
small_removed <- remove_false_pos(small_example)
knitr::kable(small_removed)
```

To see which reads were set to zero use `which_set_to_zero()`:
```{r, echo=TRUE, results='asis'}
small_set_to_zero <- which_set_to_zero(small_example, small_removed)
knitr::kable(small_set_to_zero)
```

That used the default value of 0.2 for the parameter alpha (yes??).....

## Big example

The more realistic `big_example` has ** mock samples and ** non-mock samples,
with ...

```{r, echo=TRUE, results='asis'}
knitr::kable(big_example)
```

To remove the false positives:

```{r, echo=TRUE, results='asis'}
big_removed <- remove_false_pos(big_example)
knitr::kable(big_removed)
```

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
